DATA 621 - Business Analytics and Data Mining

### 2020-12-02 Final_project/Final Project Paper - Group 2.Rmd
OK. The issue seems to be one where downloading strips some of the crazy characters. Maybe it's not using UTF-8. Therefore, everyone can download from LOCAL once they pull the data from the repo.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```
```{r loadLibraries}
library(doParallel)
library(knitr)
library(dplyr)
library(dtplyr)
library(stringr)
library(ggplot2)
library(scales)
library(caret)
library(data.table)
```
```{r loadData}
dataHeader <- "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/Final_project/Data/"
ca_path <- paste0(dataHeader, "CAvideos.csv")
us_path <- paste0(dataHeader, "USvideos.csv")
gb_path <- paste0(dataHeader, "GBvideos.csv")
fr_path <- paste0(dataHeader, "FRvideos.csv")
de_path <- paste0(dataHeader, "DEvideos.csv")
droppedFields <- c('description', 'thumbnail_link')
ca_set <- fread(ca_path, drop = droppedFields)
us_set <- fread(us_path, drop = droppedFields)
gb_set <- fread(gb_path, drop = droppedFields)
fr_set <- fread(fr_path, drop = droppedFields)
de_set <- fread(de_path, drop = droppedFields)
nobsUS <- nrow(us_set)
nobsCA <- nrow(ca_set)
nobsGB <- nrow(gb_set)
nobsFR <- nrow(fr_set)
nobsDE <- nrow(de_set)
nobsTot <- nobsUS + nobsCA + nobsGB + nobsFR + nobsDE
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```
```{r loadLibraries}
library(doParallel)
library(knitr)
library(dplyr)
library(dtplyr)
library(stringr)
library(ggplot2)
library(scales)
library(caret)
library(data.table)
```
```{r loadData}
dataHeader <- "../Final_project/Data2/"
ca_path <- paste0(dataHeader, "CAvideos.csv")
us_path <- paste0(dataHeader, "USvideos.csv")
gb_path <- paste0(dataHeader, "GBvideos.csv")
fr_path <- paste0(dataHeader, "FRvideos.csv")
de_path <- paste0(dataHeader, "DEvideos.csv")
colClass <- c(rep('character', 4L), 'integer', 'POSIXct', 'character',
              rep('double', 4L), 'character', rep('boolean', 3L), 'character')
droppedFields <- c('description', 'thumbnail_link')

# Download, expand, and ingest raw data files
ca_set <- fread(ca_path, drop = droppedFields, colClasses = colClass)

us_set <- fread(unzip(temp), drop = droppedFields)

gb_set <- fread(unzip(temp), drop = droppedFields)

fr_set <- fread(unzip(temp), drop = droppedFields)

de_set <- fread(unzip(temp), drop = droppedFields)

nobsUS <- nrow(us_set)
nobsCA <- nrow(ca_set)
nobsGB <- nrow(gb_set)
nobsFR <- nrow(fr_set)
nobsDE <- nrow(de_set)
nobsTot <- nobsUS + nobsCA + nobsGB + nobsFR + nobsDE
```
